Racial and Ethnic Differences in ETI

### 2023-07-17 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti.qmd
tidyverse formatting

```{r}
library(DataExplorer)
```

@@

```{r}
# Import
df = read.csv("~/Documents/Work/Vigers/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Raw/DataDelivery_20230420/CFF21_Annualized_Del1.csv")
# Generate report
# df %>%
#   create_report(
#     output_file = paste0("/Users/timvigers/Documents/Work/Vigers/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/Reports/Annualized EDA ", 
#                          format(Sys.time(), "%Y-%m-%d"),".html"),
#     report_title = "Annualized EDA - Racial and Ethnic Differences in ETI"
#   )
skimr::skim(df)
```

>>>>

```{r}
library(readxl)
```

@@

```{r}
# Import
df <- read.csv("/Users/timvigers/Library/CloudStorage/Dropbox/Work/Vigers/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Raw/DataDelivery_20230420/CFF21_Annualized_Del1.csv",na.strings = "")
demo = read.csv("/Users/timvigers/Library/CloudStorage/Dropbox/Work/Vigers/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Raw/DataDelivery_20230420/CFF21_DemogCFDiag_Del1.csv",na.strings = "")
dict = read_excel("/Users/timvigers/Library/CloudStorage/Dropbox/Work/Vigers/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Raw/Copy of Codes for CFFPR_2023.xlsx")
# Merge demographic data

# Factor variables
df$smoking <- factor(df$smoking,
  levels = 1:4,
  labels = c(
    "No", "Occasionally",
    "Yes, Regularly, less than 1 ppd",
    "Yes, Regularly, 1 ppd or more"
  )
)
df$second_smoke <- factor(df$second_smoke,
  levels = 1:4,
  labels = c(
    "Daily", "Several Times Per Week",
    "Several Times Per Month or less",
    "Never"
  )
)
df$cfrd_status_annual <- factor(df$cfrd_status_annual,
  levels = 1:5,
  labels = c("NGT", "IGT", "CFRD", "T1D", "T2D")
)
df$Transplant_status <- factor(df$Transplant_status,
  levels = 1:5,
  labels = c(
    "Not pertinent",
    "Accepted, on waiting list",
    "Evaluated, final decision pending",
    "Evaluated, rejected",
    "Had transplantation"
  )
)
# Format binary variables
bin_vars = c("insurance","employment")
bin_vars = colnames(df)[which(sub("\\d","",colnames(df)) %in% bin_vars)]
bin_vars = c(bin_vars,"pregnant")
df[,bin_vars] = lapply(df[,bin_vars],factor,levels = 0:1,labels = c("No","Yes"))
```
